Optimizing Abstract Abstract Machines

### 2012-11-13 paper/paper.tex
Figure showing state graphs under base, lazy, compile.

\documentclass[preprint,onecolumn,9pt]{sigplanconf} %{onecol}
\usepackage{alltt,mathpartir}
\usepackage{amsmath,amsthm}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{url}
\usepackage{graphicx}
\usepackage{balance}

@@

\begin{figure}
\begin{alltt}
(define (zero? n) ((n (\(\lambda\) (zx) #f)) #t))
(define (((mult m1) m2) mf) (m2 (m1 mf)))
(define ((((plus p1) p2) pf) x)
  ((p1 pf) ((p2 pf) x)))

@@

\section{An abstract$^{\text 2}$ machine for ISWIM}
\label{sec:aam}

>>>>

\documentclass[preprint,onecolumn,9pt]{sigplanconf} %{onecol}
\usepackage{alltt,mathpartir}
\usepackage{amsmath,amsthm}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{url}
\usepackage{graphicx}
\usepackage{balance}
\usepackage{calc}

@@

\begin{figure}
\hrule
\vspace{2mm}
\begin{alltt}
(define (zero? n) ((n (\(\lambda\) (zx) #f)) #t))
(define (((mult m1) m2) mf) (m2 (m1 mf)))
(define ((((plus p1) p2) pf) x)
  ((p1 pf) ((p2 pf) x)))

@@

\begin{figure}
\hrule
\vspace{2mm}
\begin{alltt}
(define (id x) x)
(define (f n)
  (cond [(<= n 1)  1]
        [else      (* n (f (- n 1)))]))
(define (g n)
  (cond [(<= n 1)  1]
        [else      (+ (* n n) (g (- n 1)))]))
(print (+ ((id f) 3) ((id g) 4)))
\end{alltt}
\hrule
\begin{center}
\begin{tabular}{ccc}
\raisebox{1ex-\height}{
\includegraphics[height=4in]{introspective-base.pdf}}
&
\raisebox{1ex-\height}{
\includegraphics[height=3.7in]{introspective-lazy.pdf}}
&
\raisebox{1ex-\height}{
\includegraphics[height=2.2in]{introspective-lazyc.pdf}}
\\
(a) Baseline
&
(b) Lazy
&
(c) Compiled
\end{tabular}
\end{center}
\caption{Example state graphs for the program above.  Part (a) shows
  the result of the baseline analyzer.  It has long ``corridor''
  transitions and ``diamond'' subgraphs that fan-out from
  nondeterminism and fan-in from joins.  Part (b) shows the result of
  performing nondeterminism lazily and thus avoids many of the diamond
  subgraphs.  Part (c) shows the result of abstract compilation that
  removes intepretive overhead in the form of intermediate states,
  thus minimizing the corridor transitions.  The end result is a more
  compact abstraction of the program that can be generated faster.}
\end{figure}

\newpage
\
\newpage
\section{An abstract$^{\text 2}$ machine for ISWIM}
\label{sec:aam}
